Security Audit of Safeplug

### 2014-01-08 report.tex
added some sections, but not complete
added more sections
added bib items
added info from our proposal

\documentclass[12pt, letterpaper]{article}

@@

>>>>

\documentclass[12pt, letterpaper]{article}
\usepackage{url}

@@

\section{Introduction}

\section{Background}
Safeplug is a product that launched last week from the cloud storage company Pogoplug, offering to let users browse the web with “complete security and anonymity” for the cheap price of \$49 \cite{safeplug}.  Safeplug offers Tor out of the box, with no additional software installation, by sitting between a user’s router and the internet \cite{wired}.  Pogoplug’s marketing pitch centers around the protection of user’s IP addresses by using Tor \cite{safeplug,bittech}.  Lots of folks are excited about the idea, but waiting to see a security audit, including Bruce Schneier \cite{schneier}.  Gigaom quotes Pogoplug CEO Dan Putterman as saying the box uses “vetted software” \cite{gigaom} but who knows what that means?

\section{Goals}
In this project, we would like to do a security audit of the Safeplug and investigate the following questions.  How does the box pick which relay node on the Tor network to connect to?  What kind of authentication goes on between the box and the Tor node?  Does it use the same route of Tor relays every time?
Safeplug claims to offer in-box ad-blocking.  How does this work and does it remove any functionality?  Is there an easy way to whitelist things without turning Safeplug off entirely?

What are the configurations on the box?  Is it clear to users what information is being hidden and what information is being leaked?  The website talks a lot about IP addresses and warns users to clear cookies \cite{safeplug}, but is that sufficient to preserve anonymization across all web traffic (including Flash or Javascript supercookies that might not be cleared when cookies are cleared)?  Can user anonymity be leaked by a user’s behavior while still using the Safeplug?  What else must a user do in addition to using the Safeplug to further preserve anonymity?

Safeplug can act as a relay in the Tor network \cite{techreview}; how would widespread use of the box affect the Tor network?

\section{Methodology}
Safeplug is not open source, which makes a security audit much more challenging.  This leads to a debate on where a user will put his/her trust.  Despite not having the source code, we hope to get a Safeplug, set it up via their website, and use Wireshark to capture traffic and see what happens.  Wireshark allows us to capture and analyze network data \cite{wireshark}.  We are interested both in the communication between the clients and the Safeplug and between the Safeplug and the outside world.

\section{Results}

\section{Conclusion}
